Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-06 ms/SI.Rmd
Analyze redundancy by grain size with custom function

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

>>>>

loadd(list = c(
  "richness_by_res",
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

```{r grain-size, fig.width = 7, fig.height = 3}
# Helper function to format resolution labels
degree_lab <- function (x) {
  as.numeric(x) %>% 
    scales::number(suffix = "\u00b0", accuracy = 0.1)
}

# Summarize redundancy statistics by grain size
redundancy_summary <-
  richness_by_res %>%
  mutate(above_50 = ifelse(redundancy > 0.5, 1, 0)) %>%
  mutate(singleton = ifelse(redundancy == 0, 1, 0)) %>%
  group_by(res) %>%
  summarize(
    n_total = n(),
    n_above_50 = sum(above_50),
    n_singletons = sum(singleton),
    percent_above_50 = n_above_50/n_total,
    percent_singletons = n_singletons/ n_total,
    .groups = "drop"
  )

# Percent of grid cells with redundancy > 0.5 by grain size
a <- ggplot(redundancy_summary, aes(x = res, y = percent_above_50)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = degree_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy > 0.5"
  )

# Percent of grid cells with redundancy = 0 by grain size
b <- ggplot(redundancy_summary, aes(x = res, y = percent_singletons)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = degree_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy = 0"
  )

# Distribution of redundancy by grain size
c <- ggplot(redund_by_res, aes(x = redundancy, y = res)) +
  geom_density_ridges(scale = 1.5) + 
  scale_y_discrete(expand = c(0, 0), labels = degree_lab) +     # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  labs(
    x = "Redundancy",
    y = "Resolution"
  )

a + b + c +
  plot_annotation(tag_levels = 'A')

ggsave(result_file(s_figure("grain-size"), "pdf"), width = 7, height = 3, units = "in")
```

**`r s_figure("grain-size")`**. `r s_figure_cap("grain-size")` **A**, Percent of grid cells with redundancy > 0.5 by grain size (0.1, 0.2, 0.3, or 0.4 degree grid-cells). **B**, Percent of grid cells with redundancy = 0 by grain size. **C**, Distribution of redundancy values by grain size.
